The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-08 rational.tex
_
more particle based tracing diagrams

%%%%%%%%%%%%%%%%%%%%
\subsection{Syntax} 
\label{sec:pi-syntax}

@@

The syntactic notation described in Sec \ref{sec:pi-syntax} is often
obscure and hard to read.  Following the tradition established for
monoidal categories~\cite{springerlink:10.1007/978-3-642-12821-94}, we
present a graphical language that conveys the intuitive semantics of
the language (which is formalized in the next section).  For the rest
of the paper {{langRev}} programs will be presented graphically.

@@

DIAGRAM    
  \end{multicols}

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%
\subsection{Syntax and Types} 
\label{sec:pi-syntax}

@@

The syntactic notation described in Sec \ref{sec:pi-syntax} is often
obscure and hard to read.  Following the tradition established for
monoidal categories~\cite{springerlink:10.1007/978-3-642-12821-94}, we
present a graphical language that conveys the intuitive semantics of
the language (which is formalized in the next section).  Since, the
graphical notation is easier to read an trace, for the rest of the
paper {{langRev}} programs will be presented graphically.

@@

\begin{center}
\scalebox{0.95}{
%%subcode-line{pdfimage}[diagrams/thesis/b-wire.pdf]
\includegraphics{diagrams/thesis/b-wire-value.pdf}
}
\end{center}
  \end{multicols}

@@

\begin{multicols}{2}
\begin{center}
\scalebox{0.95}{
\includegraphics{diagrams/thesis/product-one-wire-value.pdf}
}
\end{center}
\begin{center}
\scalebox{0.95}{
\includegraphics{diagrams/thesis/product-two-wires-value.pdf}
}
\end{center}
\end{multicols}

@@

\begin{multicols}{2}
\begin{center}
\scalebox{0.95}{
\includegraphics{diagrams/thesis/sum-two-wires-left-value.pdf}
}
\end{center}
\begin{center}
\scalebox{0.95}{
\includegraphics{diagrams/thesis/sum-two-wires-right-value.pdf}
}
\end{center}
\end{multicols}
